Extracellular potentials generated by axonal projections are shaped by patterns of bifurcations and terminations

### 2016-03-21 doc/manuscript.tex
caption update

\begin{figure}[htbp]
\centering
\includegraphics{../figs/fig_1.pdf}
\caption{\label{fig:simpletree}Relationship between axon structure and
extracellular potential. The top row shows simulated action potentials
travelling along a single axon with varying morphologies, as indicated
by the diagram in the left side of each subfigure. Action potential
propagation direction indicated by the arrow. All waveforms recorded at
a distance of 150\(\mu\)m from the axon, and at the depth indicated by
plot position, spaced by 200\(\mu\)m. (\textbf{A}) An action potential
in an infinitely long, straight axon. (\textbf{B}) Effect of a
terminatiing axon. Action potential waveform closest to the termination
thickened for emphasis. (\textbf{C}) Effect of a branching axon. The
axon branches multiple times in the range of 200\(\mu\)m. Thicker
waveform at the center of the bifurcation zone. \textbf{D} Combined
effect of bifurcations and terminations. Lower row shows responses of a
population of 100 randomly branching and termnating axons. Three sample
morphologies are shown to the left. \textbf{E} Extracellular waveform in
response a spike initiated simultaneously in all axons. Spike initiation
time indicated by the raster lines at the top. \textbf{F} CSD calculated
from the waveforms shown in E. \textbf{G} Response to spontaneous
activity superimposed with a pulse of hightened spike rate, averaged
over 100 trials. Example spike times shown by the raster plot at
top.\textbf{H} CSD calculated from the pulse response in G.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{../figs/fig_1.pdf}
\caption{\label{fig:simpletree}Relationship between axon structure and
extracellular potential. The top row shows simulated action potentials
travelling along a single axon with varying morphologies, as indicated
by the diagram in the left side of each subfigure. The lower row shows
responses of a population of 100 randomly branching and termnating
axons. Three sample morphologies are shown to the left of the lower row.
Action potential propagation direction indicated by the arrow. All
waveforms recorded at a distance of 150\(\mu\)m from the axon, and at
the depth indicated by plot position, spaced by 200\(\mu\)m.
(\textbf{A}) An action potential in an infinitely long, straight axon.
(\textbf{B}) Effect of a terminatiing axon. Action potential waveform
closest to the termination thickened for emphasis. (\textbf{C}) Effect
of a branching axon. The axon branches multiple times in the range of
200\(\mu\)m. Thicker waveform at the center of the bifurcation zone.
(\textbf{D}) Combined effect of bifurcations and terminations.
(\textbf{E}) Extracellular waveform in response a spike initiated
simultaneously in all axons. Spike initiation time indicated by the
raster lines at the top. (\textbf{F}) CSD calculated from the waveforms
shown in E. (\textbf{G}) Response to spontaneous activity superimposed
with a pulse of hightened spike rate, averaged over 100 trials. Example
spike times shown by the raster plot at top. (\textbf{H}) CSD calculated
from the pulse response in G.}
\end{figure}
